---
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(dplyr)

data <- readxl::read_excel("/Users/ankushidutta/Downloads/Group5 (1).xlsx")
```


## CSSAS vs graduate

```{r}
data %>%
  group_by(graduate) %>%
  summarise(
    count = n(),
    mean_CSSAS = mean(CSSAS, na.rm = TRUE),
    sd_CSSAS = sd(CSSAS, na.rm = TRUE)
  )
```

```{r}
t.test(CSSAS ~ graduate, data = data, var.equal = FALSE)
```

## CSSAS vs mplan

```{r}
data %>%
  group_by(mplan) %>%
  summarise(
    count = n(),
    mean_CSSAS = mean(CSSAS, na.rm = TRUE),
    sd_CSSAS = sd(CSSAS, na.rm = TRUE)
  )

```

```{r}
t.test(CSSAS ~ mplan, data = data, var.equal = FALSE)
```
T-Test shows a statistically significant difference in mean CSSAS scores, with non-meal-plan students reporting higher stress (p < 2.2e-16). 95% confidence interval for the difference in means was [1.34, 1.80], indicating a reliable difference between the groups.


## CSSAS vs. loans

```{r}
data %>%
  group_by(loans) %>%
  summarise(
    count = n(),
    mean_CSSAS = mean(CSSAS, na.rm = TRUE),
    sd_CSSAS = sd(CSSAS, na.rm = TRUE)
  )

t.test(CSSAS ~ loans, data = data, var.equal = FALSE)
```


## CSSAS vs. grade (Low vs High GPA)

```{r}
grade_data <- data %>%
  filter(grade %in% c(1, 4)) %>%
  mutate(gpa_group = ifelse(grade == 1, "low", "high"))

grade_data %>%
  group_by(gpa_group) %>%
  summarise(
    count = n(),
    mean_CSSAS = mean(CSSAS, na.rm = TRUE),
    sd_CSSAS = sd(CSSAS, na.rm = TRUE)
  )
```


```{r}
t.test(CSSAS ~ gpa_group, data = grade_data, var.equal = FALSE)
```

## FI vs graduate

```{r}
data %>%
  group_by(graduate) %>%
  summarise(
    count = n(),
    FI_mean = mean(FI, na.rm = TRUE),
    FI_sd = sd(FI, na.rm = TRUE)
  )

table(data$graduate, data$FI) %>% chisq.test()
```

## FI vs mplan

```{r}
data %>%
  group_by(mplan) %>%
  summarise(
    count = n(),
    FI_mean = mean(FI, na.rm = TRUE),
    FI_sd = sd(FI, na.rm = TRUE)
  )
table(data$mplan, data$FI) %>% chisq.test()
```

## FI vs loans

```{r}
data %>%
  group_by(loans) %>%
  summarise(
    count = n(),
    FI_mean = mean(FI, na.rm = TRUE),
    FI_sd = sd(FI, na.rm = TRUE)
  )
table(data$loans, data$FI) %>% chisq.test()
```

## FI vs grade (Low vs High GPA)

```{r}
grade_FI <- data %>%
  filter(grade %in% c(1, 4)) %>%
  mutate(gpa_group = ifelse(grade == 1, "low", "high"))

grade_FI %>%
  group_by(gpa_group) %>%
  summarise(
    count = n(),
    FI_mean = mean(FI, na.rm = TRUE),
    FI_sd = sd(FI, na.rm = TRUE)
  )
table(grade_FI$gpa_group, grade_FI$FI) %>% chisq.test()
```

